\section{Quickstart: anatomy of a course repo}\label{sec:quickstart}

A course lives in one repository, organised by topic, with this machinery in
a hidden subdirectory. The demo course (\file{course-demo}) is the
reference layout:

\begin{manexsource}
course-demo/
  .course-machinery/   the toolkit (classes, packages, scripts)
  .latexmkrc           puts the machinery on TEXINPUTS
  .MIRRORDIR           optional PDF mirror destination
  course-vocab.tex     per-course vocabulary
  derivatives/         a topic (a course has several, same shape)
    problems/          problem bank: one problem per file
    lectures/          LectureNotes masters (+ .latexmkrc)
    facts/             preamble-less snippets to \import
    images/
  _assessment/         Assessment masters (+ .latexmkrc)
  _syllabus/           CourseDocument masters (+ .latexmkrc)
\end{manexsource}

Three document classes cover every document a course produces -- when you
sit down to write, the only decision is which one:

\begin{itemize}
  \item \file{Assessment} -- anything graded or handed in: tests, finals,
    quizzes, homework (\texttt{[noid]}), worksheets. Clear and standard;
    nothing fancy. Section~\ref{sec:assessments}.
  \item \file{LectureNotes} -- lecture handouts, with a projector view for
    the room. Big type, board space, imported examples.
    Section~\ref{sec:lectures}.
  \item \file{CourseDocument} -- prose documents: syllabus, TA info,
    policies. Coloured headings, TOC, reading measure.
    Section~\ref{sec:prose-documents}.
\end{itemize}

Underneath them, shared packages supply the content machinery -- the same
problem environments, boxes, whitespace commands and fonts everywhere, so
one problem file moves freely between a test and a lecture. You rarely load
any of them yourself; the class does (Part~\ref{part:reference} documents
each).

\subsection{The wiring}

Documents name their class plainly -- \cs{documentclass}\texttt
{\{LectureNotes\}} -- and never spell out where it lives. The
\file{.latexmkrc} in each \file{.tex}-holding directory makes that work: it
walks up to the repo root and puts \file{.course-machinery//} on
\env{TEXINPUTS} for that build. The copies are identical; creating a new
topic folder means copying one file in.

Cross-file inclusion uses the \file{import} package's relative paths, so one
source serves every consumer. A lecture and the quiz pull the \emph{same}
\file{power-rule-basic.tex} by the path each needs -- \file{../problems/}
beside it, \file{../derivatives/problems/} from the repo root -- and any
images that file loads resolve against the \emph{file's own} directory.

The one course-wide content file is \file{course-vocab.tex} at the repo
root: the vocabulary this course's textbook uses (its named result boxes,
the noun lectures call an example). Masters \cs{input} it in the preamble
by relative path; section~\ref{sec:extending} explains what belongs there
and why it is guarded.

\subsection{The five-minute loop}

Day to day, the toolkit is a three-step loop:

\begin{enumerate}
  \item \textbf{Write or find problems.} One file per problem in a topic's
    \file{problems/}, tagged; \texttt{find-problems -{}-topic ...} to
    rummage (sections \ref{sec:problem-files}, \ref{sec:build-and-find}).
  \item \textbf{Assemble a document.} A master imports problems (with
    points, on a test; as examples, in a lecture) and declares its views
    in the \texttt{\%! views:} comment.
  \item \textbf{Build.} \texttt{build-pdfs} in the document's directory
    compiles everything there -- student PDF plus each declared view,
    routed to the synced mirror if one is configured
    (section~\ref{sec:build-and-find}).
\end{enumerate}

The rest of Part~1 walks these in order; Part~\ref{part:reference} is the
per-file reference; Part~\ref{part:architecture} explains the architecture
-- the load-order contract, the view/layer model, and how to extend the
vocabulary -- for the day you want to change the machinery itself.
