\section{Prose documents}\label{sec:prose-documents}

Syllabi, TA information sheets, course policies -- continuous prose rather
than problems -- are \file{CourseDocument} documents. It is the ``designed''
class of the three: coloured headings, a titled cover, a table of contents,
and a text measure tuned for reading. (This manual is itself a
CourseDocument.) The demo repo's \file{_syllabus/syllabus.tex}:

\begin{manexsource}
%! views: instructor
\documentclass[11pt]{CourseDocument}

\title{\course{101} --- Syllabus}
\subtitle{%
  Fall 2026, University of New Brunswick \\[1ex]
  \normalfont\normalsize\itshape Sections FR01 and FR02.
}

\begin{document}

\maketitle
\pagestyle{toc}
\tableofcontents

\newpage
\pagestyle{myfancy}

In \course[MATH]{1013} we will be investigating...

\end{document}
\end{manexsource}

That opening sequence is the documented idiom, worth copying verbatim.
\cs{maketitle} runs while the page style is still \texttt{plain}, so the
title page stays bare; the contents page then opts into \texttt{toc}
(footer page number only); and \texttt{myfancy} -- a small-caps running
head with the current section, page number in the footer -- starts with the
body. Neither named style activates itself: each document chooses when.

The pieces in play:

\begin{itemize}
  \item \cs{title} and \cs{subtitle} feed a shared title block that also
    stamps \emph{Updated \textnormal{(date, time)}} -- these documents are
    living and revised mid-term, and the stamp says which printing is
    current. The subtitle's second line above shows the usual trick for a
    quieter sub-subtitle: reset the font inline.
  \item \cs{course}\texttt{[MATH]\{1013\}} sets a course designation in
    sans with lining numerals -- consistent wherever it appears, prose or
    title. The bracket defaults to the course's own prefix, so
    \cs{course}\texttt{\{101\}} works too.
  \item Headings and internal links pick up the course identity colour --
    named \emph{once} (\env{CourseIdentity}, a mahogany) and derived
    everywhere, so restyling a course document is a one-line change.
    Deliberately \emph{not} green: green means ``solutions, not for
    students'' everywhere else in the toolkit, so a student-facing document
    must not read as green.
  \item \texttt{[legalpaper]} is available, as on assessments; stock
    \file{article} options pass through.
\end{itemize}

Body text in this class uses old-style figures -- the numerals with
ascenders and descenders you see in this manual's prose -- because these
documents are continuous reading. Dates, office numbers and the like sit
quietly in the text; \cs{liningnums}\texttt{\{2026\}} forces lining figures
where a number should read as data, and math and \cs{course} numerals stay
lining automatically. The full figure policy lives with
\file{Typefaces.sty} (section~\ref{sec:ref-typefaces}).

Two things CourseDocument deliberately lacks: the exercise system (a
syllabus imports no problems -- the class loads no Exercises/Workspace
machinery), and any use of \cs{workspace}. It \emph{does} carry the
instructor-notes layer, so a syllabus can hold staff-only annotations --
office-hour strategy, grading-scheme rationale -- and ship an
\file{-INSTRUCTOR} view like any other document
(section~\ref{sec:build-and-find}).
