\section{Building and finding: the two scripts}\label{sec:build-and-find}

Two executables ship with the machinery. \file{build-pdfs} compiles course
documents (with their views, and with output routed where you want it);
\file{find-problems} searches the problem bank. Both print their full
reference with \texttt{-{}-help}.

\subsection{\texorpdfstring{\texttt{build-pdfs}}{build-pdfs}}

\begin{manexsource}
$ build-pdfs              # compile every .tex in this directory
$ build-pdfs test.tex     # just this one (FILE.tex -> FILE.pdf)
\end{manexsource}

The script runs latexmk from each file's own directory, so relative imports
resolve and the directory's \file{.latexmkrc} puts the machinery on
\env{TEXINPUTS}. Auxiliary files (\file{.aux}, \file{.log}, \dots) go to a
per-directory folder under \file{~/.cache/latexmk/} -- they clutter neither
the repo nor the output directory -- keyed by the directory's repo-relative
path, so two topics' same-named \file{problems/} folders never share
latexmk state.

\subsubsection{Views: one source, several PDFs}

A magic comment in a source's \emph{leading} comment block (it must precede
\cs{documentclass}) requests extra PDFs:

\begin{manexsource}
%! views: solutions, hints, instructor
\documentclass[12pt,thursday]{Assessment}
\end{manexsource}

Four views are wired, each injecting a layer definition ahead of the source
so the call site needs no class option:

\begin{itemize}
  \item \env{solutions} $\to$ \file{FILE-SOLUTIONS.pdf}: defines
    \cs{ShowSolutions}, so \env{solution} bodies and the boxed MC keys
    print.
  \item \env{hints} $\to$ \file{FILE-HINTS.pdf}: defines \cs{ShowHints}.
    Independent of solutions -- a hint is student-facing help, so list both
    views if you want both PDFs.
  \item \env{projector} $\to$ \file{FILE-PROJECTOR.pdf}: defines
    \cs{ProjectorView}, switching \file{LectureNotes} to the 17\,pt room
    copy.
  \item \env{instructor} $\to$ \file{FILE-INSTRUCTOR.pdf}: the staff
    bundle -- solutions $+$ hints $+$ instructor notes, inside the
    page-edge frame. A view is a \emph{bundle of layers}; the instructor
    copy is the staff copy (TAs get it too -- there is no separate marker
    tier).
\end{itemize}

An unrecognised view name warns and is skipped; the student PDF always
builds. Under the default overlay mode, every view of a document has
identical page breaks (section~\ref{sec:overlay}).

\subsubsection{Where the PDFs go}

The output mirror is one \file{.MIRRORDIR} file, found by walking up from the
build directory to the nearest ancestor that holds one (the repo top level,
the way \file{.latexmkrc} finds the machinery). Its first bare line names a
base directory (leading \texttt{\~{}} expanded) that \emph{mirrors the repo
tree}: a source built in \file{REPO/integrals/lectures} ships its PDF to
\file{BASE/integrals/lectures}. The mirror subdirectory is created if absent,
but the base itself must exist -- if the cloud drive is unmounted, the script
warns and builds locally rather than scattering a stray tree. By default the
PDF goes \emph{straight there}, with no local copy; add a line reading
\texttt{BOTH} to build locally \emph{and} copy. Blank and \texttt{\#}-comment
lines are ignored; the base path and the \texttt{BOTH} keyword may come in
either order. A nearer \file{.MIRRORDIR} in a subdirectory wins, letting a
subtree mirror somewhere else. With no \file{.MIRRORDIR} above it at all, the PDF
lands next to its source.

\file{SAMPLE-MIRRORDIR}, shipped with the machinery, is the commented template --
copy it to \file{.MIRRORDIR} and uncomment. \file{.MIRRORDIR} is meant to be
git-ignored: each machine points its own way.

\paragraph{Routing a view to a named folder.}
Sometimes one view of a document belongs somewhere else too -- the instructor
copy of a test in a folder shared with TAs, say, while the rest of the build
still mirrors to your private cloud. Add \texttt{LABEL: path} lines to
\file{.MIRRORDIR} and tag the view with a matching \texttt{:LABEL} suffix in the
magic comment:

\begin{manexsource}
%! views: solutions, instructor:TA-dir
\end{manexsource}

\noindent That drops \file{FILE-INSTRUCTOR.pdf}, flat, into the directory
\texttt{TA-dir:} names \emph{in addition} to the mirror; \env{solutions} still
goes only to the mirror. The labelled directory must already exist (a missing
label or directory warns and skips just that extra copy -- the build still
succeeds and still mirrors). Because the source names only a \emph{label} and
the git-ignored \file{.MIRRORDIR} maps it to a path, no machine-specific path ever
enters a tracked source. The pseudo-view \env{default} names the base (student)
PDF itself, so \texttt{default:LABEL} routes it the same way; a bare
\env{default} is a harmless no-op.

Routing decides \emph{where} a view goes, not \emph{when} it is released: if
you would rather TAs not see solutions until after the assessment, point the
label at a private staging folder and copy across by hand at release time --
\file{build-pdfs} deliberately knows nothing about dates.

\subsection{\texorpdfstring{\texttt{find-problems}}{find-problems}}

\begin{manexsource}
$ find-problems [--topic PAT] [--tag PAT] [--difficulty PAT]
                [--source PAT] [--untagged] [--vocab] [--import]
                [DIR ...]
\end{manexsource}

Reads the \cs{ProblemMeta} block off every \file{.tex} file under each
\env{DIR} (default: the current directory, recursively) and reports the
matches -- without running LaTeX, which is the point
(section~\ref{sec:problem-files}). With no filters, it lists every file
that has a block.

The four filters combine with AND. \env{PAT} is an extended regular
expression matched case-insensitively against each comma-separated item, so
\texttt{-{}-topic power} finds \texttt{power-rule} and
\texttt{-{}-topic '\^{}power-rule\$'} matches exactly. A filter on a key a
file does not set never matches -- \texttt{-{}-difficulty basic} will not
sweep in untagged files.

Three modes round it out:

\begin{itemize}
  \item \texttt{-{}-vocab} ignores the filters and prints the tag and topic
    vocabulary in use, with counts -- the antidote to a bank where half the
    problems say \emph{integration} and half say \emph{integrals}. Read it
    before inventing a tag.
  \item \texttt{-{}-untagged} inverts: files with \emph{no} metadata block
    at all -- the tagging backlog.
  \item \texttt{-{}-import} prints the matches as \cs{import} lines ready
    to paste into a document.
\end{itemize}

The parser is textual and deliberately simple, which is where the
one-key-per-line discipline of section~\ref{sec:problem-files} comes from:
a reflowed block still compiles, but this script no longer sees it.
