\section{CourseBoxes.sty}\label{sec:ref-courseboxes}

Theorem-like boxes in two families, both built on amsthm heads inside
tcolorbox frames:

\begin{itemize}
  \item \textbf{Text results} -- things that live in the course text and
    carry the number the text gives them. The number is \emph{declared}
    (typed at the call site), not counted, so the machinery is
    numbering-scheme-agnostic; \cs{label}/\cs{ref} record the typed number.
  \item \textbf{Asides} -- the instructor's pedagogical interjections.
    Unnumbered, and deliberately not \cs{label}-able: a stray label prints
    \texttt{[unlabelled aside]} -- loud -- rather than silently grabbing
    the section number.
\end{itemize}

Load-order contract: amsthm must already be loaded, which Typefaces'
newtxmath owns -- so CourseBoxes comes \emph{after} Typefaces (enforced by
a \cs{PackageError}); hyperref (for the boxes' link anchors) arrives via
Hyperlinks in time for body use. Section~\ref{sec:load-order} has the whole
ordering story.

\subsection*{Shipped vocabulary}

Universal text results (every textbook has them):
\env{theorem}, \env{proposition}, \env{lemma}, \env{corollary} (italic
body); \env{definition}, \env{example}, \env{remark} (upright body). Call
site: \texttt{\char`\\begin\{theorem\}\{2.1.3\}[Power Rule]}.

Shared asides (the author's voice, consistent course to course):
\env{caution} (red, warning glyph), \env{takeaway} (blue),
\env{yourturn} (blue, pen glyph), \env{prepwork} (blue, book glyph), and
\env{tip}\texttt{[surviving$\vert$thriving]} (orange; the optional tier
appends ``for the \emph{surviving/thriving}'' to the head).

Text-\emph{specific} vocabulary (Key Idea, Axiom, \dots) deliberately does
not ship here -- it is declared per course in \file{course-vocab.tex} with
the factories below (section~\ref{sec:extending}).

\subsection*{The factories}

\begin{center}
\begin{tabularx}{\linewidth}{@{}l Y@{}}
\cs{NewTextResult}\texttt{[head]\{env\}\{Name\}\{box\}} & declare a
  numbered text result; call site
  \texttt{\char`\\begin\{env\}\{num\}[name]}. Default head \env{cbdefn}
  (upright); pass \env{cbthm} for italic.\\
\cs{NewAside}\texttt{[head]\{env\}\{Name\}\{box\}} & declare an unnumbered
  aside. Default head \env{cbaside} (black sans).\\
\end{tabularx}
\end{center}

\subsection*{Restyling knobs}

Named once, referenced everywhere -- each is a one-line edit:

\begin{center}
\begin{tabularx}{\linewidth}{@{}l Y@{}}
tcolorbox styles & \env{cb/textresult} (quiet grey L-rule),
  \env{cb/note} (blue box), \env{cb/caution} (red), \env{cb/tip}
  (orange).\\
amsthm head styles & \env{cbthm}, \env{cbdefn}, \env{cbaside},
  \env{cbnote}, \env{cbnotecolon} (colon punctuation), \env{cbcaution},
  \env{cbtip}. Head punctuation is the style's sixth argument.\\
colours & \env{ThmColor} (grey), \env{NoteColor} (royal blue),
  \env{CautionColor} (red), \env{TipColor} / \env{TipTextColor}
  (orange; the darker text value keeps WCAG contrast). Provisional
  pending a colour-blind-safe palette pass; the head glyphs
  (fontawesome, monochrome) are the colour-independent channel.\\
\end{tabularx}
\end{center}
