\section{LectureNotes.cls}\label{sec:ref-lecturenotes}

The lecture class: handouts and their projector twin, from one source.
Based on \file{extarticle} for the large sizes -- 14\,pt handout, 17\,pt
projector. Loads Exercises, ProblemMeta, Workspace, Typefaces (lining),
MathStuff, Titling, Hyperlinks, CourseBoxes and InstructorNotes -- the full
stack. Workflow: section~\ref{sec:lectures}.

\subsection*{Class options}

\begin{center}
\begin{tabularx}{\linewidth}{@{}l Y@{}}
\texttt{projector} & the in-room copy: 17\,pt, tighter top margin, no
  marginpar column, no page number, grey back-to-top arrow in the footer.
  Normally you never write it -- the build's \env{projector} view injects
  \cs{ProjectorView} and the class switches by itself.\\
\emph{(other)} & forwarded to \file{extarticle}.\\
\end{tabularx}
\end{center}

\subsection*{Commands and hooks}

\begin{center}
\begin{tabularx}{\linewidth}{@{}l Y@{}}
\cs{NotesProblemLabelWord} & the noun imported problems render as
  (default \emph{Example}); redefine per \emph{text}, in
  \file{.textbook/textbook.tex}. Routed into \cs{ProblemLabelWord} so a
  shared text layer cannot disturb Assessment's fixed ``Q''.\\
\end{tabularx}
\end{center}

\subsection*{Presentation choices}

Imported problems render with a run-in bold heading, unnumbered by default:
\textbf{Example.}\ -- plus the literal \texttt{number=} and parenthetical
\texttt{desc=} if the import supplied them (``Example 2.1.8 (from
APEX).'').\ The problem counter still steps invisibly, so cross-references
stay sound. The \env{problemgroup} stem takes the same unnumbered form.
Points keys are ignored -- notes are ungraded.

Other deliberate class behaviour:

\begin{itemize}
  \item \cs{subsectionbreak} is \cs{clearpage}: every subsection starts a
    fresh page (a lecture subsection is a screenful/boardful).
  \item Only \cs{section} is numbered (\env{secnumdepth} 1); the TOC shows
    three levels.
  \item Paragraph spacing is airier than the parskip default
    (\texttt{skip=1em}) -- room to annotate, legible from the back row.
  \item No running head; the handout has a centred page number, the
    projector copy none (it is scrolled, not paged -- hence the back-to-top
    footer arrow instead).
  \item Headings and links stay black: lectures sit with assessments on
    the ``clear, not fancy'' side; colour belongs to CourseDocument.
\end{itemize}
