\section{TextRef.sty}\label{sec:ref-textref}

Links from the notes into the course textbook. The package holds the
\emph{mechanism} only; the base URL and the section list are course data,
declared in the course's text layer (\file{.textbook/textbook.tex},
section~\ref{sec:extending}). Loaded by all three classes, and inert
until that file is \cs{input}.

\begin{center}
\begin{tabularx}{\linewidth}{@{}l Y@{}}
\cs{SetTextBase}\texttt{\{URL\}} & where the text lives; every slug is
  appended to it verbatim, so include the trailing slash. Default: empty
  (no text declared).\\
\cs{DeclareSection}\texttt{\{5.2\}\{slug.html\}} & one manifest entry:
  section number $\to$ its page. Last declaration wins.\\
\cs{textbookref}\texttt{\{5.2\}\{Table 5.2.3\}} & prints
  ``Table 5.2.3'', linked to \S5.2.\\
\cs{textbookref*}\texttt{\{5.2.6\}\{Example\}} & starred: appends the key,
  so this prints ``Example~5.2.6''.\\
\end{tabularx}
\end{center}

\subsection*{Three decisions that shape it}

\textbf{Keyed on the section, never finer.} Table 5.2.3, Key Idea 5.2.1
and Example 5.2.6 all resolve to the top of \S5.2, and the student
scrolls. Page URLs are the stable part of a web text; in-page anchors are
exactly what rots. So the manifest is about forty lines for a course
rather than several hundred, and it survives a re-edition that renumbers
items \emph{within} a section. A full coordinate is accepted anyway --
\cs{textbookref}\texttt{\{5.2.3\}} truncates to \texttt{5.2} on a miss --
so you can type what you read off the page.

\textbf{Graceful degradation is the point.} The label text always prints.
It becomes a link only if the manifest resolves the key \emph{and}
hyperref is loaded. A missing text layer, a typo'd key, or an Assessment
master (which deliberately loads no hyperref -- a link on paper is a dead
end) all demote the reference to correct plain text. Nothing breaks, and
nothing is silently wrong.

\textbf{Misses are reported.} Degrading silently would let a whole rotted
manifest pass unnoticed, since the document still compiles and still
reads correctly. So each unresolved key gets one \cs{PackageInfo} in the
\file{.log} (deduplicated -- a section cited twenty times logs once), and
the end of the run warns with the full list:

\begin{manexsource}
Package TextRef Warning: Textbook references printed WITHOUT links
(no matching \DeclareSection):
(TextRef)                9.9, 10.4.
\end{manexsource}

\subsection*{The layering rule}

\cs{textbookref} is a \emph{text-tied} citizen, and the model only holds
if it stays where the text is known:

\begin{itemize}
  \item \textbf{Yes:} lecture bodies, box titles at the call site, and
    import-time \env{desc=}.
  \item \textbf{No:} inside \file{CourseBoxes.sty} or
    \file{Exercises.sty} -- that would couple text-agnostic machinery to
    a particular manifest.
  \item \textbf{No:} inside a \file{problems/} or \file{facts/} file.
    Those are reused across courses and texts; a baked-in reference would
    point at the wrong book the moment the file is borrowed.
\end{itemize}

The reference therefore goes in the lecture \emph{around} the import,
where the text is known and \file{Exercises.sty} merely re-emits it:

\begin{manexsource}
\importfact[number={2.1}, desc={from \textbookref{2.1}{APEX 2.1}}]%
  {../facts/}{power-rule.tex}
\end{manexsource}

\subsection*{One text layer per master}

A course may draw its chapters from more than one book -- an opening
review chapter out of one text, the rest out of another. Mount one text
layer per book. But \textbf{every master \cs{input}s exactly one of
them}, and never two.

That costs nothing, because it is how notes are written anyway: a lecture
guides students through \emph{one} book. And the two things that would
collide fail very differently, which is the reason to be deliberate
rather than to find out:

\begin{itemize}
  \item \textbf{Vocabulary collides loudly.} \cs{NewTextResult}
    (section~\ref{sec:ref-courseboxes}) ends in
    \cs{NewDocumentEnvironment}, which \emph{errors} on a name already
    taken. Two layers that both name a result stop the build. Annoying,
    but it tells you.
  \item \textbf{Links collide silently.} \cs{DeclareSection} is
    last-declaration-wins, so a second layer's \texttt{1.1} quietly
    replaces the first's. Both books have a \S1.1; they are different
    sections. The document compiles, reads correctly, and links to the
    wrong book.
\end{itemize}

Last-wins is not an oversight -- it is what lets a course-local
declaration override one it inherits, which is worth more than an error
on duplicates. So the discipline lives here, in the rule, rather than in
a check.

\subsection*{Why no URL registry}

The eventual link-checker (harvest every external link, \texttt{curl}
them, report rot on your schedule rather than in front of a class) reads
the \emph{sources}: one file of \cs{DeclareSection} lines, plus every
\cs{demo} call (section~\ref{sec:ref-titling}). It does not read anything
this package writes at compile time, and there is deliberately nothing to
write. Same discipline as ProblemMeta and FactMeta: ``what does this
course contain?'' must be answerable without running \LaTeX.
