\section{build-pdfs and find-problems}\label{sec:ref-scripts}

Both scripts are documented in workflow terms in
section~\ref{sec:build-and-find}; this is the terse recap. Each prints its
full header with \texttt{-{}-help}.

\subsection*{build-pdfs}

\begin{manexsource}
build-pdfs [FILE.tex ...]    # no args: every .tex in the cwd
\end{manexsource}

\begin{center}
\begin{tabularx}{\linewidth}{@{}l Y@{}}
views & \texttt{\%!\ views: solutions, hints, projector, instructor} in
  the leading comment block; each produces \file{FILE-VIEW.pdf} by
  injecting its layer definition(s). Unknown views warn and skip. A
  \texttt{:LABEL} suffix also drops that view, flat, into the named
  \file{.MIRRORDIR} destination (\env{default} = the base PDF).\\
output & nearest ancestor \file{.MIRRORDIR} (bare base path $+$ optional
  \texttt{BOTH}) tree-mirrors the repo under the base $\to$ else local.
  Base must exist; missing $\to$ warn and fall back to local.
  \texttt{LABEL: path} lines name flat per-view destinations (must exist).
  \file{SAMPLE-MIRRORDIR} is the template.\\
aux files & \file{~/.cache/latexmk/}$\langle$\emph{repo-relative
  key}$\rangle$-$\langle$\emph{job}$\rangle$.\\
\end{tabularx}
\end{center}

\subsection*{find-problems}

\begin{manexsource}
find-problems [--topic PAT] [--type PAT] [--difficulty PAT]
              [--source PAT] [--untagged] [--vocab] [--tsv]
              [--import [--with LIST] [--from DIR]] [PATH ...]
\end{manexsource}

\begin{center}
\begin{tabularx}{\linewidth}{@{}l Y@{}}
\texttt{-{}-topic}, \texttt{-{}-type}, \texttt{-{}-difficulty},
  \texttt{-{}-source} & AND-combined filters; PAT is a case-insensitive
  ERE matched per comma-separated item.\\
\texttt{-{}-vocab} & print the type/topic vocabulary with counts (filters
  ignored).\\
\texttt{-{}-untagged} & files with no \cs{ProblemMeta} block -- the
  backlog.\\
\texttt{-{}-import} & matches as paste-ready \cs{importproblem} lines.\\
\texttt{-{}-with LIST} & (with \texttt{-{}-import}) inject metadata keys as
  options; \env{LIST} is a comma subset of \env{number,desc}, added where a
  file has them. \env{points} stays manual.\\
\texttt{-{}-from DIR} & (with \texttt{-{}-import}) make each line's directory
  argument relative to \env{DIR}, the importing document's folder.\\
\texttt{-{}-tsv} & one tab-separated row per match
  (path, desc, topics, type, difficulty, source, number) -- the machine feed
  for \file{pick-problems}. Respects the filters.\\
\end{tabularx}
\end{center}

A \env{PATH} operand may be a directory (walked recursively) or a single
\file{.tex} file, so a picker can ask \texttt{-{}-import} about exactly the
files it selected.

\subsection*{pick-problems}

\begin{manexsource}
pick-problems [--from DIR] [FILTER ...] [PATH ...]
\end{manexsource}

An fzf front-end to \file{find-problems}: it feeds \texttt{-{}-tsv} into fzf
(multi-select, metadata shown, the \file{.tex} previewed with \file{bat}), then
turns the chosen problems into paste-ready \cs{importproblem} lines via
\texttt{-{}-import}, printed to standard output. \texttt{-{}-from} is forwarded
to the emitter; every other argument is forwarded to the \texttt{-{}-tsv} feed,
so \file{find-problems}' filters pre-narrow what the picker offers. The Vim
command \texttt{:ImportProblem} (\texttt{<Space>ip}, in
\file{after/ftplugin/tex.vim}) is the same pipeline wired to insert at the
cursor, with \texttt{-{}-from} set to the editing buffer's own directory.

\subsection*{find-facts and pick-facts (the fact-bank twins)}

The fact bank (section~\ref{sec:ref-factmeta}) is searched and imported by the
same machinery, one rung smaller. \file{find-facts} and \file{pick-facts} behave
exactly like their problem counterparts above but read \cs{FactMeta} blocks and
emit \cs{importfact} lines, over the fact schema: the filters are
\texttt{-{}-topic} and \texttt{-{}-source} only (a fact has no type or
difficulty), and \texttt{-{}-tsv} columns are
(path, desc, topics, source, number). The Vim command \texttt{:ImportFact}
(\texttt{<Space>if}) mirrors \texttt{:ImportProblem}.

Under the hood all four commands are thin shims over one shared engine,
\file{find-meta} (\file{find-problems}/\file{find-facts}) and \file{pick-meta}
(\file{pick-problems}/\file{pick-facts}): a \texttt{-{}-kind} selects the block
macro, the emitted wrapper and the key schema; the reading, matching and
emitting are written once. Run any shim with \texttt{-{}-help} for its concrete
flags.
