\section{FactMeta.sty}\label{sec:ref-factmeta}

Greppable \emph{fact} metadata -- ProblemMeta's little sibling, and like it
\emph{store-only} and nice-to-have. A fact is a bare snippet (a definition, a
formula) with no structure of its own; FactMeta lets you find one by what it
says without running \LaTeX. One command:

\begin{manexsource}
\FactMeta{
  source = {apex},
  number = {2.1},
  topics = {differentiation, power-rule},
  desc   = {},
}
\end{manexsource}

Keys: \env{source}, \env{number}, \env{topics}, \env{desc} -- a strict subset of
ProblemMeta's. A fact has \emph{no} \env{type} or \env{difficulty} (those
describe a \emph{problem}'s form and challenge), and nothing extrinsic like
points. \env{topics} lists every subject the fact touches (and echoes its
folder); \env{source}/\env{number} are a provenance origin and its locator;
\env{desc} is an optional short label. On the \LaTeX{} side the block is
\emph{validated but discarded}: a mistyped key errors at compile time, nothing is
typeset. The real reader is \file{find-facts}, which parses the block textually
off disk -- hence the same two disciplines (one key per line with braced values,
and \texttt{\#} written \texttt{\char`\\\#}) as ProblemMeta.

Design notes worth keeping in mind:

\begin{itemize}
  \item \textbf{Intrinsic only.} Source, number and topics belong to a fact
    forever. Anything set at the import site is not a key here.
  \item \textbf{Keys reset per block}, so a file that omits \env{number} never
    inherits a previous import's value when several facts land in one document.
  \item \textbf{Removable.} If tagging is abandoned, delete the package:
    Exercises' \cs{AtBeginDocument} stub swallows leftover \cs{FactMeta} blocks
    and every document still builds.
  \item \textbf{Import wrapper.} A picked fact is inserted as
    \cs{importfact}\texttt{[number, desc]\{DIR\}\{FILE\}} (defined in
    \file{Exercises.sty}, beside \cs{importproblem}). By default it renders the
    fact bare; the injected \env{number}/\env{desc} are captured into
    \cs{CurrentFactNumber}/\cs{CurrentFactDesc} but shown only if a document
    opts in by redefining the \cs{ShowFactMeta} hook -- e.g.\ a formula sheet
    that wants ``Power Rule\ldots{} \S2.1'' beside each fact. This mirrors the
    ProblemMeta margin display that once existed: metadata captured and
    available, display opt-in.
\end{itemize}
