\section{ProblemMeta.sty}\label{sec:ref-problemmeta}

Greppable problem metadata -- \emph{store-only}, and the nice-to-have half
of the exercise system (Exercises works without it). One command:

\begin{manexsource}
\ProblemMeta{
  topics     = {differentiation, power-rule},
  type       = {polynomial, routine},
  difficulty = {basic},
  source     = {stewart-8e},
  number     = {3.1.2},
  desc       = {},
}
\end{manexsource}

Keys: \env{topics}, \env{type}, \env{difficulty}, \env{source},
\env{number}, \env{desc}. \env{topics} lists every subject the problem
touches (and echoes its folder); \env{type} is its form or character;
\env{source}/\env{number} are a clean provenance origin and its locator;
\env{desc} is an optional short content label, sparse by design.
On the LaTeX side the block is \emph{validated but discarded}: a mistyped
key errors at compile time; nothing is typeset. The real reader is
\file{find-problems}, which parses the block textually off disk -- hence
the two disciplines (one key per line with braced values, and \texttt{\#}
written \texttt{\char`\\\#}) explained in section~\ref{sec:problemmeta}.

Design notes worth keeping in mind:

\begin{itemize}
  \item \textbf{Intrinsic only.} Topics, type, difficulty, source and
    number belong to a problem forever. Points do not -- they are
    extrinsic, set at the import site, and deliberately not a key here.
  \item \textbf{Keys reset per block}, so a file that omits \env{source}
    never inherits the previous import's value when several problems land
    in one document.
  \item \textbf{Removable.} If tagging is abandoned, delete the package:
    Exercises' \cs{AtBeginDocument} stub swallows leftover blocks and every
    document still builds.
  \item A display layer (metadata printed in the margin of staff copies)
    existed and was removed once no view wanted it; git history has it if
    it is ever missed.
\end{itemize}
